Analysis of split plot design using MCMCglmm

### 2018-04-25 README.Rmd
add statement about data-raw to README
Update static docs

This repository is our research compendium for our analysis of the effects of
alternate wetting and drying irrigation technology on rice sheath blight
disease. The compendium contains all data, code, and text associated with the
publication. The `Rmd` files in the `analysis/paper/` directory contain details
of how all the analyses reported in the paper were conducted, as well as
instructions on how to rerun the analysis to reproduce the results. The
`data/` directory in the `analysis/` directory contains all the raw data.

@@

## Required packages
 - agricolae
 - bookdown
 - car
 - carData
 - dplyr (>= 0.7.0)
 - fitdistrplus
 - forcats
 - ggplot2
 - ggpubr
 - kableExtra
 - knitr
 - lattice
 - lubridate
 - MASS
 - MCMCglmm
 - reshape2
 - rmarkdown
 - plotMCMC
 - purrr (>= 0.2.3)
 - tibble
 - tidyr (>= 0.7.0)

>>>>

This repository is our research compendium for our analysis of the effects of
alternate wetting and drying irrigation technology on rice sheath blight
disease. The compendium contains all data, code, and text associated with the
publication. The `Rmd` files in the `analysis/paper/` directory contain details
of how all the analyses reported in the paper were conducted, as well as
instructions on how to rerun the analysis to reproduce the results. The
`data/` directory in the `analysis/` directory contains all the raw data. The
`data-raw` directory contains a README.Rmd, which when knit generates the data
used in the analysis of the paper and places `.rda` files in `data/` for the
analysis.

@@
